Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-11-01 doc/RMD/mlg-mcg.Rmd
update visualization a bit

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  mutate(comm = case_when(
    .$community == 7 ~ "A",
    .$community == 5 ~ "B",
    .$community == 1 ~ "C",
    TRUE ~ as.character(.$community)
  )) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", comm), "Other Communities (n < 10)")) %>%
  mutate(comm = comm) # It just so happens that the communities are in order by size.
lay2$community <- the_communities$comm
mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.005, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = community, 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_linetype_manual(values = c(1, 3)) +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("black", "black", "white", "white")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
  # ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r severity, fig.width = 7, fig.height = 4}
count_group <- . %>% 
  mutate(nobs = n()) %>%  # count the number of samples/MCG
  ungroup() %>%
  arrange(desc(nobs)) # arrange by number of samples and reorder factors 
Severity <- filter(strat, MCG %in% mcgs$MCG[1:5]) %>%
  group_by(MCG) %>% 
  count_group %>%
  mutate(MCG = forcats::fct_inorder(factor(MCG), ordered = TRUE)) %>%
  mutate(MLG = ifelse(MLG %in% mlgs$MLG[1:5], paste("MLG", MLG), "Other"))

severity_plot <- ggplot(Severity, aes(x = MCG, y = Severity)) +
  geom_point(aes(fill = MLG), 
             position = position_jitter(width = 0.2),
             alpha = 0.75,
             pch = 21) +
  scale_fill_viridis(discrete = TRUE, direction = -1) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(aspect.ratio = 0.6) +
  facet_wrap(~Region, nrow = 2) +
  ylim(c(3.5, 8)) +
  labs(list(
    title = "Severity by MCG and Region",
    fill = "Multilocus Haplotype",
    subtitle = "Five most abundant multilocus genotypes shown"
  ))
severity_plot
if (!interactive())
  ggsave(severity_plot, filename = "results/figures/publication/FigureS3.pdf", width = 183, unit = "mm")
```

>>>>

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  mutate(comm = case_when(
    .$community == 7 ~ "A",
    .$community == 5 ~ "B",
    .$community == 1 ~ "C",
    TRUE ~ as.character(.$community)
  )) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", comm), "Other Communities (n < 10)")) %>%
  mutate(comm = comm) # It just so happens that the communities are in order by size.
lay2$community <- the_communities$comm
mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.005, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = community, 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_linetype_manual(values = c(1, 3)) +
  # scale_alpha_manual(values = c(1, 0.4)) +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("black", "black", "white", "white")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  theme(legend.box.spacing = unit(-1, "lines")) +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines"))
  # ggtitle("Relation of Multilocus Genotypes and MCGs")

@@

```{r severity, fig.width = 7, fig.height = 4}
count_group <- . %>% 
  mutate(nobs = n()) %>%  # count the number of samples/MCG
  ungroup() %>%
  arrange(desc(nobs)) # arrange by number of samples and reorder factors 
Severity <- filter(strat, MCG %in% mcgs$MCG[1:8]) %>%
  group_by(MCG) %>% 
  count_group %>%
  mutate(MCG = forcats::fct_inorder(factor(MCG), ordered = TRUE)) %>%
  mutate(MLG = ifelse(MLG %in% mlgs$MLG[1:5], paste("MLG", MLG), "Other"))

severity_plot <- ggplot(Severity, aes(x = MCG, y = Severity)) +
  geom_point(aes(fill = MLG), 
             position = position_jitter(width = 0.2),
             alpha = 0.75,
             pch = 21) +
  scale_fill_manual(values = c(viridis(5, direction = -1), NA)) +
  theme_bw() +
  theme(legend.position = "bottom") +
  theme(aspect.ratio = 0.6) +
  facet_wrap(~Region, nrow = 2) +
  ylim(c(3.5, 8)) +
  labs(list(
    title = "Severity by MCG and Region",
    fill = "Multilocus Haplotype",
    subtitle = "Five most abundant multilocus genotypes shown"
  ))
severity_plot
if (!interactive())
  ggsave(severity_plot, filename = "results/figures/publication/FigureS3.pdf", width = 183, unit = "mm")
```
